Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
in the middle

% In Theorem \ref{thm:llevel-2}, we show a policy with
Our second policy achieves an instance-dependent regret
guarantee. This policy has the same info-graph structure as the first
one in Theorem \ref{thm:llevel-1}, but requires a higher number of
levels $L = O(\log(T/\log\log(T)))$ and larger group sizes. We will
bound its regret as a function of the gap parameter $\Delta$ even
though the construction of the policy does not depend on $\Delta$. In
particular, this regret bound outperforms the one in Theorem
\ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.  It
also has the desirable property that the policy does not conceal too
much information from agents---any agent $t$ observes a good fraction
of history in previous rounds.

\begin{theorem}
\label{thm:llevel-2}
There exists a $O(\log(T)/\log\log(T))$-level policy such that for
every multi-armed bandit instance with gap parameter $\Delta$, the
policy has regret $$O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$$
Moreover, under this policy, each agent $t$ observes a subhistory of
size at least $\Omega( t/\polylog(T))$.
\end{theorem}
\swcomment{think the theorem statement implies independence of
  $\Delta$}

@@

We will now present the main idea of extending from 3-level to
$L$-level is that instead of using the second level as one
``check-point'', we use more levels to have multiple ``check points''.
Some new challenges appear in this process. Here we give an overview
of the additional techniques we use to get our $L$-level results.

\xhdr{Connecting structures between levels.} In our 3-level
policy, the second level has $\NG = \Theta(\log(T))$ groups. We do so to
ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with
high probability, both arms are pulled enough times in the second
level. The argument relies on the fact that agents in different
second-level groups observe disjoint histories of the first level and
the independent randomness in first level groups guarantees each arm
$a$ to have a ``lucky'' second-level group such that agents in that
group all pull arm $a$ with high probability.

@@

In order to avoid this undesirable factor, we design a slightly different connecting structure between levels in our $L$-level policy. The key observation is that, for any level $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level groups to see disjoint histories of the $(l-1)$-th level to ensure that there is some ``lucky'' group for each arm whose mean is close enough to the best arm. However, it does not matter much if pulls in levels below $l-1$ get observed by agents in different $l$-th level groups because group sizes in lower levels are much smaller than group sizes of level $l-1$ and the independent randomness in level $l-1$ is sufficient.

>>>>

% In Theorem \ref{thm:llevel-2}, we show a policy with
Our second policy achieves an instance-dependent regret
guarantee. This policy has the same info-graph structure as the first
one in Theorem \ref{thm:llevel-1}, but requires a higher number of
levels $L = O(\log(T/\log\log(T)))$ and larger group sizes. We will
bound its regret as a function of the gap parameter $\Delta$ even
though the construction of the policy does not depend on $\Delta$. In
particular, this regret bound outperforms the one in Theorem
\ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$.  It
also has the desirable property that the policy does not withhold too
much information from agents---any agent $t$ observes a good fraction
of history in previous rounds.

\begin{theorem}
\label{thm:llevel-2}
There exists a $O(\log(T)/\log\log(T))$-level policy such that for
every multi-armed bandit instance with gap parameter $\Delta$, the
policy has regret $$O_K(\min(1/\Delta, T^{1/2}) \cdot \polylog(T))$$
Moreover, under this policy, each agent $t$ observes a subhistory of
size at least $\Omega( t/\polylog(T))$.
\end{theorem}

Note for constant number of arms, this result mathches the optimal
regret rate (given in \Cref{eq:model-OptRegret}) for stochastic
bandits, up to logarithmic factors.

@@

A natural idea to extend the three-level policy is to insert more
levels as multiple ``check points", so the policy can incentivize the
agents to perform more adaptive exploration. However, we need to
introduce two main modifications in the info-graph two accomendate
some new challenges. We will first informally describe our techniques
the two-arm case.

% \begin{description}
% \item[Challenge 1] \emph{Exponentially growing number of groups.} 
% \item[Challenge 2] \emph{Uncertain number of arm pulls.}  
% \end{description}

\OMIT{We will now present the main idea of extending from 3-level to
  $L$-level is that instead of using the second level as one
  ``check-point'', we use more levels to have multiple ``check
  points''.  Some new challenges appear in this process. Here we give
  an overview of the additional techniques we use to get our $L$-level
  results.}

\paragraph{Interlacing connections between levels.}A tempted approach
to generalize the three-level policy is to build an $L$-level
info-graph with the structure of a $\NG$-ary tree: for every
$l\in \{2, \ldots , L\}$, each $l$-level group observes the
sub-history from a disjoint set $\NG$ groups in level $(l-1)$. The
disjoint sub-histories observed by all the groups in level $l$ are
independent, and under the small gap regime (similar to
Lemma~\ref{3levelsmallcase}) it ensures that each arm $a$ has a
``lucky'' $l$-level group of agents that only pull $a$. This ``lucky''
property is crucial for ensuring that both arms will be explored in
level $l$.

However, in this construction, the first level will have $\NG^{L-1}$
groups, which incurs $\NG^{\Omega(L)}$ regret. The exponential
dependence in $L$ will heavily limit the adaptivity of the policy, and
prevents having the number of levels for obtaining the result in
\Cref{thm:llevel-2}. To overcome this, we will design an info-graph
structure such that the number of groups at each level stays as
$\sigma^2 = \Theta(\log^2(T))$.

We will leverage the following key observation: in order to maintain
the ``lucky'' property, it suffices to have agents in different $l$-th
level groups to observe disjoint sub-histories that takes place in
level $(l - 1)$. Moreover, as long as the group size in levels lower
than $(l-1)$ are substantially smaller than group size of level $l-1$,
the ``lucky'' property does not break even if different groups in
level $l$ observe overlapping sub-history from levels
$\{1, \ldots, l-2\}$.

\OMIT{In our 3-level policy, the second level has
  $\NG = \Theta(\log(T))$ groups. We do so to ensure that in the small
  gap case (Lemma \ref{3levelsmallcase}), with high probability, both
  arms are pulled enough times in the second level. The argument
  relies on the fact that agents in different second-level groups
  observe disjoint histories of the first level and the independent
  randomness in first level groups guarantees each arm $a$ to have a
  ``lucky'' second-level group such that agents in that group all pull
  arm $a$ with high probability.

@@

  In order to avoid this undesirable factor, we design a slightly
  different connecting structure between levels in our $L$-level
  policy.  The key observation is that, for any level
  $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level
  groups to see disjoint histories of the $(l-1)$-th level to ensure
  that there is some ``lucky'' group for each arm whose mean is close
  enough to the best arm. However, it does not matter much if pulls in
  levels below $l-1$ get observed by agents in different $l$-th level
  groups because group sizes in lower levels are much smaller than
  group sizes of level $l-1$ and the independent randomness in level
  $l-1$ is sufficient.}
